---
title: "Projects"
format: html
---

Projects in GitHub the topic `czieoss6-biocgpu`

```{bash projects, echo = FALSE}
TOPIC=czieoss6-biocgpu
LIMIT=100
gh search repos --visibility public --topic ${TOPIC} --include-forks false --limit ${LIMIT} > /tmp/projects.txt
```

```{r read-projects, echo = FALSE, message = FALSE}
library(BiocPkgTools)

devel <- BiocPkgTools::biocPkgList(version = "devel")
release <- BiocPkgTools::biocPkgList(version = "release")
columns <- c("repository", "description", "visibility", "updated")
projects <- read.csv("/tmp/projects.txt", sep = "\t", col.names = columns,
                     header = FALSE)
```

```{r list-projects, echo = FALSE, message = FALSE}
library(dplyr)
library(DT)

df <- data.frame(package = gsub("^.*/", "", projects$repository),
                 repository = paste0("https://github.com/", projects$repository),
                 description = projects$description,
                 owner = gsub("/.*$", "", projects$repository),
                 updated = as.Date(projects$updated, format = "%Y-%m-%d"))
df <- df |>
  dplyr::mutate(in_bioc = package %in% release$Package | package %in% devel$Package) |>
  dplyr::mutate(bioc_url = ifelse(in_bioc,
                                  paste0("https://bioconductor.org/packages/", package),
                                  ""))

logo <- "<svg xmlns='http://www.w3.org/2000/svg' width='16' height='16' fill='currentColor' class='bi bi-github' viewBox='0 0 16 16'> <path d='M8 0C3.58 0 0 3.58 0 8c0 3.54 2.29 6.53 5.47 7.59.4.07.55-.17.55-.38 0-.19-.01-.82-.01-1.49-2.01.37-2.53-.49-2.69-.94-.09-.23-.48-.94-.82-1.13-.28-.15-.68-.52-.01-.53.63-.01 1.08.58 1.23.82.72 1.21 1.87.87 2.33.66.07-.52.28-.87.51-1.07-1.78-.2-3.64-.89-3.64-3.95 0-.87.31-1.59.82-2.15-.08-.2-.36-1.02.08-2.12 0 0 .67-.21 2.2.82.64-.18 1.32-.27 2-.27.68 0 1.36.09 2 .27 1.53-1.04 2.2-.82 2.2-.82.44 1.1.16 1.92.08 2.12.51.56.82 1.27.82 2.15 0 3.07-1.87 3.75-3.65 3.95.29.25.54.73.54 1.48 0 1.07-.01 1.93-.01 2.2 0 .21.15.46.55.38A8.012 8.012 0 0 0 16 8c0-4.42-3.58-8-8-8z'/> </svg>"

display_df <- data.frame(Repository = paste0(ifelse(df$in_bioc, paste0("<a href='", df$bioc_url, "'>"), ""), 
                                             df$package,
                                             ifelse(df$in_bioc, "</a> ", ""),
                                             " <a href='",df$repository, "'>", 
                                             logo,
                                             "</a>"),
                         Description = df$description,
                         Owner = df$owner,
                         "Last updated" = df$updated)

DT::datatable(display_df, escape = FALSE)
```

## Support for maintainers

The grant funded work to create a new Bioconductor build system
(BBS) report for GPU-capable software packages running on machines at the
University of Padova, the Dana Farber Cancer Institute, and Jetstream2:
* [devel BBS GPU Report](https://bioconductor.org/checkResults/devel/bioc-gpu-LATEST/)
* [release BBS GPU Report](https://bioconductor.org/checkResults/release/bioc-gpu-LATEST/)

Bioconductor package maintainers can who have packages capable of using GPUs
can opt in to the build report by adding a `.BBSoptions` file with
`GPU_reliance: required` or `GPU_reliance: optional` as described in the
[contributions guide](https://contributions.bioconductor.org/advanced-build-options.html#gpu-builds).

## Support for users

Additionally, users can search for packages tagged as
[GPU](https://bioconductor.org/packages/devel/BiocViews.html#___GPU) in biocViews.
